One-arm spirals in locally isothermal, radially structured self-gravitating discs

### 2014-11-07 paper/results_3d.tex
update

\subsection{Vertical motion}
In Fig. \ref{3d_vert} we measure three-dimensionality using the
parameter $\Theta$ as defined in Eq. \ref{theta}. Vertical velocities
do increase with the growth of the one-arm spiral. Larger amplitudes
are reached in ZEUS because of larger numerical noise. 
However, even 
in this case, $\Theta \lesssim 10^{-2}$. This implies $|v_z/c_s|\lesssim
0.2$ for $h=0.05$. Thus, vertical motions are sub-sonic and negligible
compared to horizontal motions.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/m1_analysis_plot_vert.ps}
  \caption{Evolution of three-dimensionality $\Theta$, as defined by
    Eq. \ref{theta}, which corresponds to the
    average vertical kinetic energy density, scaled by 
    the average horizontal kinetic energy.\label{3d_vert}} 
\end{figure}

\subsection{Angular momentum evolution}

>>>>

\subsection{Vertical motion}
We measure three-dimensionality using the parameter $\Theta$ as
defined in Eq. \ref{theta}.  Vertical velocities
do increase with the growth of the one-arm spiral, 
%Larger amplitudes
%are reached in ZEUS because of larger numerical noise. 
but we find  $\Theta \lesssim 10^{-2}$. This implies $|v_z/c_s|\lesssim
0.2$ for $h=0.05$. Thus, vertical motions are sub-sonic and negligible
compared to horizontal motions. This supports the 2D approximation.

%\begin{figure}
%  \includegraphics[width=\linewidth]{figures/m1_analysis_plot_vert.ps}
% \caption{Evolution of three-dimensionality $\Theta$, as defined by
%    Eq. \ref{theta}, which corresponds to the
%   average vertical kinetic energy density, scaled by 
%    the average horizontal kinetic energy.\label{3d_vert}} 
%\end{figure}   
\subsection{Angular momentum evolution}
